\chapter{Protocol Specification}\label{appndx-protocol}
\section{Protocol Syntax}
%\begin{singlespace}  
%\vspace{0cm}
%\renewcommand{\baselinestretch}{1.0}
\begin{center}
%\renewcommand{\baselinestretch}{1.0}

\begin{supertabular}{|l|l|}
\hline
\bf{Client} & \bf{Server} \\
\hline
HELO hostname:pid & \\
Optional header& \\
Optional header& \\
. & 200 Welcome hostname:pid \\
& .\\
\hline
CONF &\\
. & 201 Config follows\\
& Config file contents\\
& Config file contents\\
&.\\
\hline
NEXT (optional no) &\\
. & 202 URLs follow\\
& URL linking\_URL\\
& URL linking\_URL\\
& URL linking\_URL\\
&.\\
&205 No Work \\
\hline
FINISHED url & \\
url found &\\
url found &\\
url found &\\
.&203 Thanks\\
&.\\
\hline
ALLOWED url &\\
.&203 OK to crawl\\
&.\\
&205 Denied by filters\\
&.\\
\hline
ROBOTS hostname &\\
.& 201 Robots.txt follows\\
&Robots.txt file contents\\
&Robots.txt file contents\\
&Robots.txt file contents\\
&.\\
&209 Not yet\\
&.\\
\hline
ROBOTSFILE hostname&\\
Robots.txt file contents&\\
Robots.txt file contents&\\
Robots.txt file contents&\\
.&203 Thanks\\
&.\\
\hline
STATS & \\
statname1: value &\\
statname2: value &\\
statname3: value &\\
statname4: value &\\
.&203 Thanks\\
&.\\
\hline
MONITOR &\\
.&210 Statistics Follow \\
&Stat1Name: Stat1Value \\
&Stat2Name: Stat2Value\\
&.\\
\hline
WORK
&.205 No Work\\
&.\\
&206 Work\\
&no of clients to fork\\
&.\\
\hline
FAILED url&\\
Optional Reason&\\
.&203 Thanks\\
&.\\
\hline
NOOP&\\
.&203 OK\\
&.\\
\hline
QUIT&\\
.&208 Bye!\\
&<DISCONNECT>\\
\hline
CHECKPOINT&\\
.&203 Ok, checkpointed\\
&.\\
\hline
PAUSE&\\
&.203 Ok\\
&.\\
&209 Already paused!\\
&.\\
\hline
START&\\
.&203 Ok\\
&.\\
&209 Not paused!\\
&.\\
\hline
STOP&\\
.&203 Ok\\
&.\\
\hline
FINGERPRINT md5sum&\\
URL&\\
.&201 Seen Already\\
&OtherURL\\
&.\\
&209 First Time Seen\\
&.\\
\hline
CHECKPOINT&\\
.&203 Ok\\
&.\\
\end{supertabular}
%\renewcommand{\baselinestretch}{1.5}
\end{center}
%\renewcommand{\baselinestretch}{1.5}
%\end{singlespace}

\section{Verb Descriptions}
\subsection{HELO}
I am a client, ready to do work. Here is my unique crawler name

\subsection{CONF}
I'd like to know what my configuration should be. Can you please tell me it?

\subsection{NEXT}
Could I have some URLs to work on please? If followed by an integer, this is the number of URLs I'd like to work on, if possible.

\subsection{FINISHED}
I've finished parsing this URL. Here are the links it contained - you should add these to your queue for filtering and crawling

\subsection{ROBOTS}
Do you have the robots.txt file for hostname?

\subsection{ROBOTSFILE}
Here is the contents of the robots.txt file for hostname that I fetched. Please save it in your cache.

\subsection{STATS}
Here are my stats, add these to your totals.

\subsection{MONITOR}
Please give me all your available stats.

\subsection{WORK}
Is there any work available yet? I'd like to fork some clients to do some work for you.

\subsection{NOOP}
No operation - just checking the connection is OK. Meaningless verb.

\subsection{ALLOWED}
Can you check that this URL is allowed by the URL filters?

\subsection{FINGERPRINT}
Here is the fingerprint of this URL. Can you check if you've seen it before and if so where?

\subsection{CHECKPOINT}
Please checkpoint your data structures to disk now.

\subsection{QUIT}
This process is shutting down (or at least disconnecting). Please disconnect me.
\subsection{PAUSE}
Temporarily pause the crawl. May not have effect in partitioned crawls. Crawlers may timeout during an extended pause.
\subsection{START}
End a pause started using the PAUSE.
\subsection{STOP}
Terminate the crawl. May take some time to have effect in partitioned crawls.

\section{Notes}
Only HELO, NOOP and QUIT are permitted if a client hasn't logged on yet. HELO is called to logon. Additional permissions are viewable in Table \ref{tbl-commands}.

\section{Return Messages}
Return messages by the dispatcher are of the form:
\begin{verbatim}
StatusNumber[space]Friendly Error Message
Optional parameters
.
\end{verbatim}
Generally speaking 2xx should be success error messages, and 3xx for messages.\\
\begin{center}
\begin{tabular}{|l|}
\hline
\bf{Generic (Error) Messages}\\
\hline
300 Client Error (produced in software by the client)\\
301 Unknown Command\\
302 Unimplemented Command\\
303 Permission Denied. (Client has insufficient privileges to execute command)\\
304 Bad Syntax\\
\hline
\end{tabular}
\end{center}
